|

### 2022-04-18 Memo/memo.Rmd
capitalise some words

Below we discuss in more detail these changes and the several others we have
made to the manuscript in response to comments from the editors and reviewers.
We thank the editors again for the opportunity to revise the manuscript, and
the reviewers for their extremely helpful comments.

>>>>

Below we discuss in more detail these changes and the several others we have
made to the manuscript in response to comments from the Editors and Reviewers.
We thank the Editors again for the opportunity to revise the manuscript, and
the Reviewers for their extremely helpful comments.
